Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-09-29 doc/paper.Rmd
change of paper structure

---
title: "Adapting toolmark based chumbley score to bullets"
author: "Ganesh Krishnan, Heike Hofmann"
date: "September 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

---
title: Adaption of the Chumbley Score to matching of bullet striation marks

# to produce blinded version set to 1
blinded: 0

authors: 
- name: Ganesh Krishnan
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX

- name: Heike Hofmann
  affiliation: Department of ZZZ, University of WWW

keywords:
- 3 to 6 keywords
- that do not appear in the title

abstract: |

bibliography: bibliography
biblio-style: apsr

output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: template.tex

---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures/',
  echo=FALSE
)
options(knitr.table.format = "latex")
```

## Introduction

What is the chumbley score?
